---
title: "Assessment - 2"
author: "Prateeksha 4658793"
date: "10/09/2021"
output: html_document
---
## *Prateeksha* **4658793**

------------------------------------

# Assignment 2

------------------------------------

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(knitr)
library(skimr)
```


### Load dataset and naming it as  ilovefood.

```{r}
ilovefood <- read.csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-11-20/thanksgiving_meals.csv")
```

### Display the first 10 rows of the dataset using RMarkdown

```{r 10 rows}
ilovefood %>% head(10) %>% 
  kable()
```

### Use fct_reorder and parse_number functions to create a factor variable family_income

```{r }
ilovefood <- ilovefood %>%
       mutate(family_income = fct_reorder(family_income, parse_number(family_income)))
```

### Generate the general statistics of the dataset using summary() and skim() function.

```{r }
skim(ilovefood) %>% 
  kable()
summary(ilovefood) %>% 
  kable()
```

### What is the number of people who celebrate?

```{r}
ilovefood %>% filter(celebrate == "Yes") %>% 
count(celebrate, sort = TRUE) %>% 
  kable()
```


### What are categories and stats for each main dish served and the method it is prepared?
### Create a data viz showing this in the most evident way. Provide your own legend and use themes.


```{r }
ilovefood %>%  count(main_dish, main_prep, sort = TRUE) %>% 
  filter(main_dish != "NA") %>% 
  ggplot(aes(n,main_prep,fill = n)) +
  geom_col() +
  facet_wrap(~main_dish) 
```

### How many use cranberry sauce? How many use gravy?

```{r}
ilovefood %>%  count(cranberry, sort = TRUE) %>% 
  kable()
ilovefood %>% filter(gravy == "Yes") %>% 
  count (gravy,sort = TRUE) %>% 
  kable() 
```


### What is the distribution of those who celebrate across income ranges
### Present this information in the most evident way on the data viz.

```{r}
ilovefood %>% filter(celebrate == "Yes") %>%  
  count(family_income, celebrate, sort = TRUE) %>% 
  ggplot(aes(n, family_income, fill = n)) +
  geom_col()
```


### What are the most common pies, sides, and desserts?

```{r }
pie <- ilovefood %>% 
  select(starts_with("pie"), -pie13) %>% 
  gather(type, value) %>% 
  count(type, value, sort = TRUE) %>% 
  na.omit(value) %>% 
  filter(type == "pie9")
sides <- ilovefood %>% 
  select(starts_with("side")) %>% 
  gather(type, value) %>% 
  count(type, value, sort = TRUE) %>% 
  na.omit(value) %>% 
  filter(type == "side9")
desserts <- ilovefood %>% 
  select(starts_with("dessert")) %>% 
  gather(type, value) %>% 
  count(type, value, sort = TRUE) %>% na.omit(value) %>% 
  filter(value != "None") %>% 
  filter(type == "dessert8")
  
```



### Present this information on a data viz


```{r}
commonfoods <- rbind(pie, sides, desserts) 
commonfoods %>% ggplot(aes(type, n, fill = value)) +
  geom_col() 
```

### How do the servings differ by income?
### Present this information on a data viz.

```{r}
ilovefood %>% count(main_dish, family_income)%>%
  na.omit(main_dish)%>%
  na.omit(family_income)%>% 
  ggplot(aes(main_dish, n, fill = family_income)) +
  geom_col() +
  facet_wrap(family_income~.,)+
  coord_flip() 
```

